---
title: "DIYFunction_HuffW"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 
2. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
3. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here


```{r}
number_sign <- function(number){
  if (number > 0){
    print("Your number is positive!")
  }
  else if (number == 0){
    print("Your number is zero!")
  }
  else {
    print("Your number is negative!")
  }
}

number_sign(number = -7)
number_sign(0)
number_sign(7)

```

```{r}
absolute_value <- function(number){
  if (number < 0){
    return(number*(-1))
  }
  else if (!is.numeric(number)){
    return("Please pass a numerical value to this function!")
  }
  else{
    return(number)
  }
}

absolute_value(-7)
absolute_value(0)
absolute_value(7)
absolute_value("Yo!")

```
```{r}

```

